\documentclass[11pt]{article}
\input{preambule}
\usepackage{listings}
\lstset{numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=5pt}

\author{Rb87}
\title{Read Me }
\date{}
\begin{document}
\maketitle
\tableofcontents

\section{Menus}
\subsection{General Info}
Menus are handled by the \texttt{menus.php} file. Each plugin has its own entry. There are two types of entries : \emph{menu} and \emph{submenu}. Each \emph{menu} is associated to a CPT, \emph{submenus} are not. Each \emph{menu} and \emph{submenu} entry call a function named \texttt{menu\_name\_page\_setup} lying inside \texttt{menu\_name/index\_menu\_name.php}.\\
\noindent
They are loaded if the corresponding plugin is activated, this is handle by the option \texttt{activated\_plugins}. \\

There is one exception : the \texttt{RbWeb} menu, which is always present. It corresponds to the settings page that handle all other menus. It calls the function \texttt{Handle\_all\_menus} in the \texttt{activated\_plugins.php} file. 



List of \emph{menus} and \emph{submenus}
\begin{enumerate}
\item Publications
\begin{enumerate}
\item Arxiv
\item Bibtex
\item Orcid
\item HAL
\item zotero
\end{enumerate}
\item Members
\item Teams
\item Jobs
\end{enumerate}

\subsection{How to add menu}

In order to add a new \emph{menu}:
\begin{enumerate}
\item In \texttt{menus.php} add the following 
\begin{lstlisting}
if (in_array('NEW',get_option("activated_plugins"))){
  add_action('admin_menu', 'add_menu_for_NEW');
    function add_menu_for_NEWr() {
      add_menu_page('NEW', //Menu Name
	'NEW', // Menu label
	'manage_options', // capability
	'NEW',// slug
	'NEW_page_setup',//function to call -> /NEW_folder/index_NEW.php
	'NEW', // icon
	'11'//position
	 	);
	}
}
\end{lstlisting}
Every 'NEW' must be changed. 

\item In \texttt{activated\_plugins.php} add, inside the \texttt{Handle\_all\_menus} functions
\begin{lstlisting}
<div>
  <?php on_off_button('Name of the NEW menu','id of the NEW menu');?>
</div>
\end{lstlisting}
\texttt{id of the NEW menu}  will be included in the option \texttt{activated\_plugins}.
\texttt{Name of the NEW menu} is just the label written on the button. 
\item In \texttt{index.php} add :
\begin{lstlisting}
if (in_array('id of the NEW menu',get_option("activated_plugins"))){
	include(plugin_dir_path(__FILE__).'NEW_folder/index_NEW.php');

}
\end{lstlisting}
the "id of the NEW menu" must be the same as the one included in the  \texttt{activated\_plugins.php} file. 

\item Create a NEW\_folder, within a \texttt{index\_NEW.php} file, that must include the \texttt{NEW\_page\_setup} function

\item Update the ReadMe file list of menus. 

\end{enumerate}

\subsection{Technical informations}
Menus and plugins activations go through an ajax call. The 'send' button is useless, only used to refresh the page. Maybe it's not the best idea ? 

\subsubsection{How ajax call work  ? }
\begin{enumerate}
\item PHP file.  Include the javascript file 
\begin{lstlisting}
function add_NEW_script(){
  wp_register_script( 'NEW Slug of script', plugin_dir_url(__FILE__).'js/NEWname_of_file.js',array('jquery') -- dependencies not mandatory);
  wp_enqueue_script( NEW Slug of script' );
  }
\end{lstlisting}
\footnote{Still does not understand the utily of the two functions \texttt{register} and \texttt{enqueue}}
and use the hook for admin script :
\begin{lstlisting}
add_action( 'admin_enqueue_scripts', 'add_NEW_script' );
\end{lstlisting}

\item PHP file (PHP$\rightarrow$ JS) Localize the script... that means you can pass PHP data to javascript. In the \texttt{add\_NEW\_script} function you add :
\begin{lstlisting}
wp_localize_script( 'NEW Slug of script', 'NEW_name_of_variable_localized', 
	array( 'ajaxurl' => admin_url( 'admin-ajax.php' ), 'var2'=>php data ));
\end{lstlisting}
Now you can use in the javascript script the \texttt{NEW\_name\_of\_variable\_localized} list of variables. 

\item JS file (JS, JS$\leftrightarrow$PHP) Create the ajax script :
\begin{lstlisting}
jQuery( document ).ready( function($) {
    php_data = NEW_name_of_variable_localized.var2 // This is where the 
		    localize is usefull !  (PHP->JS)
    $.ajax({
      url : NEW_name_of_variable_localized.ajaxurl,  
      // method : 'POST', // GET par defaut
      action  : NEW_ajax_action_name // (JS->PHP, this is where you can make
      	 the php through JS )
      success : function( return_data ) { // 
        // console.log(return_data); (PHP->JS)
      },
      error : function( data ) { // en cas d'echec    
        console.log( 'Erreur...' );
      }
    });

});
\end{lstlisting}

\item (PHP) Register the \texttt{NEW\_ajax\_action\_name} and link it to your favorite php function 
\begin{lstlisting}
add_action( 'wp_ajax_NEW_ajax_action_name$', 'NEW_call_back_function' );
\end{lstlisting}


\item (PHP) And finally create \texttt{NEW\_call\_back\_function} :
\begin{lstlisting}
function NEW_call_back_function(){		
  do php stuff, send JSON info :
  wp_send_json_success( $php data );
}
\end{lstlisting}



For the menu case here are the references of the preceeding function : 
\begin{itemize}
\item add\_NEW\_script = activated\_plugin\_script\_and\_style (activated\_plugins.php)
\begin{itemize}
\item  NEW Slug of script = activated\_button\_js 
\item NEWname\_of\_file = activated\_button\_js.js (in plugin\_dir\_url(\_\_FILE\_\_).'js/)
\item NEW\_name\_of\_variable\_localized = adminAjax
\end{itemize}
\item NEW\_ajax\_action\_name = activated\_button 
\item NEW\_call\_back\_function = activate\_plugin\_ajax
\end{itemize}





\end{enumerate}


\subsection{List of functions and files}

PHP 

\begin{itemize}
\item \texttt{index.php}
use only for including other php file. 


\item \texttt{menus.php}
\begin{itemize}
\item \texttt{add\_menu\_for\_rbWeb}
\item \texttt{add\_menu\_for\_publication}
\begin{itemize}
\item \texttt{add\_submenu\_for\_arxiv}
\item \texttt{add\_submenu\_for\_Bibtex}
\item \texttt{add\_submenu\_for\_zotero}
\item \texttt{add\_submenu\_for\_orcid}
\item \texttt{add\_submenu\_for\_hal}
\end{itemize}
\item \texttt{add\_menu\_for\_member}
\item \texttt{add\_menu\_for\_job}
\item \texttt{add\_menu\_for\_team}
\end{itemize}
\item \texttt{activated\_plugins.php}
\begin{itemize}
\item \texttt{activated\_plugin\_script\_and\_style}
\item \texttt{activate\_plugin\_ajax} (ajax callback function) 
\item \texttt{ on\_off\_button(\$name,\$id)} ( on/off button for the rbWeb plugin setting page, \$name$\rightarrow$ label shown, \$id once chosen it has to be similar in other pages eg. in index.php )
\begin{itemize}
\item \texttt{hide\_and\_show\_buttons()} (js function)
\end{itemize}
\item \texttt{Handle\_all\_menus} 
\end{itemize}


\end{itemize}

JS 
\begin{itemize}
\item \texttt{activated\_button\_js.js}
\begin{itemize}
\item \texttt{hide\_and\_show\_buttons}
\item ajax call for updating option \texttt{activated\_plugins}
\end{itemize}
\end{itemize}

CSS 
\begin{itemize}
\item \texttt{css\\activated\_button\_css.css} (style the on/off buttons)

\end{itemize}


\section{Publications}
\subsection{•}





\end{document}
